%-------------------------
% Resume in LateX
% Author : Anmol Tomer
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
%\input{glyphtounicode}  % REMOVED - not needed for LuaLaTeX

\pagestyle{fancy}
\fancyhf{} % Clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1: #2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://anmoltomer.github.io/}{\Large Anmol Tomer}} & Email: \href{mailto:anmol3540@gmail.com}{anmol3540@gmail.com}\\
  \href{https://anmoltomer.github.io/}{anmoltomer.github.io} & Mobile: \href{tel:+917389126962}{+91-738-912-6962} \\
  \href{https://www.linkedin.com/in/anmol-tomer/}{linkedin.com/in/anmol-tomer} & \href{https://github.com/AnmolTomer}{github.com/AnmolTomer} \\
  \href{https://anmoltomer.bearblog.dev/blog/}{Blog} & \href{https://leetcode.com/u/AnmolTomer/}{leetcode.com/AnmolTomer}
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Vellore Institute of Technology}{Chennai, IN}
      {Bachelor of Technology in Electronics and Computer Science Engineering; CGPA: 8.6/10.0}{2018 -- 2022}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {CRED}{Bengaluru, IN}
      {Backend Engineer}{June 2022 -- Present}
      \resumeItemListStart
        \resumeItem{\textbf{Backend Engineer, Payments Platform} (June 2023 -- Present)}
        \resumeItemListStart
            \resumeItem{Worked on Payments Loading, Merchant Onboarding and Compliance.}
            \resumeItem{Owned UPI and Payment Provider Integrations.}
        \resumeItemListEnd
        \resumeItem{\textbf{Product \& Partner Engineering} (September 2021 -- June 2023)}
         \resumeItemListStart
            \resumeItem{Contributed to building CRED pay.}
            \resumeItem{Owned sales engineering, merchant integration and onboarding automation.}
            \resumeItem{Operated in a multi-stakeholder role, working closely with product, business, tech and ops teams.}
        \resumeItemListEnd
      \resumeItemListEnd

    \resumeSubheading
      {Nokia Networks and Solutions}{Chennai, IN}
      {Data Science Intern}{May 2019 -- June 2019}
      \resumeItemListStart
        \resumeItem{Analyzed patterns in the usage of spare parts from historical data.}
        \resumeItem{Performed extensive Data Cleaning and Exploratory Data Analysis to assess usage patterns and estimate the lifespan of spare parts.}
        \resumeItem{Built Machine Learning models to predict the ideal order size for various shop floor components.}
        \resumeItem{Presented and demonstrated solutions to senior executives.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{V.A.N.I. -- Voice Analytics Interface}{Worked on a project to detect dyslexia in children at an early stage, by determining their reading age. Worked with NGOs and schools for gifted children on this project, final outcome led to a filed patent for the application. \href{https://patentscope.wipo.int/search/en/detail.jsf?docId=IN276072258&tab=NATIONALBIBLIO}{\textbf{Patent Link}}}
     \resumeSubItem{iPark -- Intelligent Parking System}{A solution to the problem of diminishing parking spaces in urban areas using Deep Learning and Computer Vision. Qualified as Top 30 for on-site finals out of 600 teams in the hackathon hosted by IISc Bangalore.} 
     \href{https://github.com/AnmolTomer/iPark}{\textbf{Github Link}} | \href{https://www.youtube.com/watch?v=3VMOG8u6cUI}{\textbf{Project DEMO}}
    \resumeSubItem{Custom Object Detection for Autonomous Rover}{Built a model for custom object detection using the Darknet Neural Network Framework for the Indian Rover Challenge 2020.}
  \resumeSubHeadingListEnd

%--------SKILLS------------
\section{Skills}
  \resumeSubHeadingListStart
    \item{
      \textbf{Languages: }{C/C++ (STL), Java, Python, SQL, JavaScript/Node.js}
    }
    \item{
      \textbf{Frameworks \& Libraries: }{FastAPI, Django, Flask, Pandas, Express.js}
    }
    \item{
      \textbf{Databases: }{MySQL, MongoDB, Redis, AWS DynamoDB}
    }
    \item{
      \textbf{Cloud \& DevOps Tools: }{AWS (EC2, S3, SQS, Lambda, Step Functions), Docker, Datadog, Jenkins, Grafana (Loki), Git}
    }
  \resumeSubHeadingListEnd

\end{document}